An efficient acyclic contact planner for multiped robots

### 2018-02-19 final.tex
cleaning figures and comrpessing images to fit limit
removed 2 figures to make room

\newcommand{\fratop}[2]{\genfrac{}{}{0pt}{}{#1}{#2}}
\newcommand{\mx}[1]{\mathbf{\bm{#1}}} 				% Matrix symbol
\newcommand{\vc}[1]{\mathbf{\bm{#1}}} 					% Vector symbol
\newcommand{\degree}{\ensuremath{^\circ}}				% define the degree symbol
\newcommand{\pder}[2]{\frac{\partial#1}{\partial#2}}		% partial derivative
\newcommand{\ppder}[2]{\frac{\partial^2 #1}{\partial#2^2}}		% second partial derivative
\newcommand{\refframe}[1]{\mbox{\textless#1\textgreater}}	% to denote a reference frame
%\DeclareMathOperator*{\lexmin}{\text{lex}\!\min}			% lexmin
\DeclareMathOperator*{\argmin}{\arg\!\min}				% argmin
\DeclareMathOperator*{\argmax}{\arg\!\max}				% argmax
\DeclareMathOperator*{\st}{subject\,to}					% subject to
\DeclareMathOperator*{\minimize}{minimize}				% 
\DeclareMathOperator*{\maximize}{maximize}				% 
\DeclareMathOperator*{\find}{find}						% 
\DeclareMathOperator*{\dif}{\mathrm{d}}					% d
\DeclareMathOperator*{\half}{\frac{1}{2}}					% one half
\newcommand{\equilibriumfeasibility}[0]{\glslink{equilibrium feasible}{\textit{equilibrium feasibility}}}	% matrix
\newcommand{\contactreachability}{\textit{contact reachability}}	% matrix
\newcommand{\mat}[1]{\ensuremath{\begin{bmatrix}#1\end{bmatrix}}}	% matrix
\newcommand{\rank}[1]{\text{rank}(#1)}							% rank
\newcommand{\diag}[1]{\text{diag}(#1)}							% diag
\newcommand{\x}{\ensuremath{\times}}
\newcommand{\spac}{\ensuremath{\quad}}						% alias for space in math environment
\newcommand{\dx}[0]{\ensuremath{\delta x}}					% dx
\newcommand{\du}[0]{\ensuremath{\delta u}}					% du
\newcommand{\DX}[0]{\ensuremath{\Delta X}}						% DX
\newcommand{\DU}[0]{\ensuremath{\Delta U}}						% DU
\newcommand{\T}[0]{\ensuremath{\top}}							% transpose symbol
\newcommand{\pinv}[0]{\ensuremath{\dagger}}					% pseudoinverse symbol
\newcommand{\Rv}[1]{\ensuremath{\mathbb{R}^{#1}}}				% set of real-valued vectors
\newcommand{\R}[2]{\ensuremath{\mathbb{R}^{#1\times #2}}}		% set of real-valued matrices
\newcommand{\Spd}[1]{\ensuremath{\mathbb{S}_+^{#1}}}			% set of symmetric positive-definite matrices
\newcommand{\card}[1]{\ensuremath{\left\vert{#1}\right\vert}}			% cardinality of a set
\DeclareMathOperator{\Tr}{Tr}							% trace
\newcommand{\Expect}{{\rm I\kern-.3em E}}				% expectation
\newcommand{\Normal}{\mathcal{N}}					% normal distribution
\newcommand{\Prob}[1]{\text{P}(#1)}						% probability

@@

%\algnewcommand{\algorithmicgoto}{\textbf{go to}}%
%%\algnewcommand{\Goto}[1]{\algorithmicgoto~\ref{#1}}%
%\algnewcommand{\Goto}{\algorithmicgoto\xspace}%
%\algnewcommand{\Label}{\State\unskip}

@@

\newcommand{\commentt}[2]{\textcolor{#1}{\textbf{\textit{[#2]}}}} 	% make sure no comments left in the paper
%\newcommand{\commentt}[2]{}							% using this line rather than the previous one you remove all comments
\newcommand{\adnote}[1]{\commentt{blue}{AD: #1}}
\newcommand{\nmnote}[1]{\commentt{OliveGreen}{NM: #1}}

% Another method to track changes
% Examples of usage:
% - This is \added[id=per,remark={we need this}]{new} text.
% - This is \deleted[id=per,remark=obsolete]{unnecessary}text.
% - This is \replaced[id=per]{nice}{bad} text.
% To print the list of change use: \listofchanges
\usepackage{changes}	% use this for the working version
%\usepackage[final]{changes} % use this for the final version
\definechangesauthor[name={Andrea Del Prete}, color=orange]{adp}
\newcommand{\deladp}[1]{\deleted[id=adp]{#1}}
\newcommand{\addadp}[1]{\added[id=adp]{#1}}
\newcommand{\repadp}[2]{\replaced[id=adp]{#1}{#2}}
\definechangesauthor[name={Steve Tonneau}, color=blue]{st}
\newcommand{\delst}[1]{\deleted[id=st]{#1}}
\newcommand{\addst}[1]{\added[id=st]{#1}}
\newcommand{\repst}[2]{\replaced[id=st]{#1}{#2}}
\newcommand{\gls}[1]{\textit{#1}}
\newcommand{\glslink}[2]{{#2}}

@@

\begin{figure*}[h!t!]
  \begin{center}
  \includegraphics[trim={7.0cm 0.0cm 20.0cm 0.0cm}, clip, width=\widthValue]
    {./video/stairclimbing1.jpeg}
  \includegraphics[trim={7.0cm 0.0cm 20.0cm 0.0cm}, clip, width=\widthValue]
    {./video/stairclimbing2.jpeg}
  \includegraphics[trim={7.0cm 0.0cm 20.0cm 0.0cm}, clip, width=\widthValue]
    {./video/stairclimbing3.jpeg}
  \includegraphics[trim={7.0cm 0.0cm 20.0cm 0.0cm}, clip, width=\widthValue]
    {./video/stairclimbing4.jpeg}
  \includegraphics[trim={7.0cm 0.0cm 20.0cm 0.0cm}, clip, width=\widthValue]
    {./video/stairclimbing5.jpeg}
  \includegraphics[trim={7.0cm 0.0cm 20.0cm 0.0cm}, clip, width=\widthValue]
    {./video/stairclimbing6.jpeg}
  \includegraphics[trim={7.0cm 0.0cm 20.0cm 0.0cm}, clip, width=\widthValue]
    {./video/stairclimbing7.jpeg}
  \caption{
           HRP-2 in the stair climbing scenario. }
		   \label{fig:stair_robust}
  \end{center}
  \vspace{-0.5cm}
\end{figure*}

@@

\subsubsection{HyQ -- Obstacle race (Figure~\ref{fig:HyQ_bridge} and~\ref{fig:HyQ_obs})}
In this long scene, HyQ has to cross a 55-cm large hole, followed by a narrow ``bridge'', only 25-cm large.

\begin{figure}
  \centering
  \includegraphics[width=0.4\linewidth]{figures/HyQ_bridge}
  \caption{
           HyQ crossing a narrow bridge. }
		   \label{fig:HyQ_bridge}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=1\linewidth]{figures/HyQ_obs}
  \caption{
           Crossing a hole contact sequence for HyQ. }
		   \label{fig:HyQ_obs}
\end{figure}

@@

\begin{figure}[!tbp]
  \centering
	\begin{overpic}[width=1\linewidth]{figures/EFORT/ellipsoid}
		\put (8.5,1.2) {\small{Velocity ellipsoid}}
		\put (62.5,1.2) {\small{Force ellipsoid} \tiny{(scale 0.5)}}
	\end{overpic}
  \caption{Examples of velocity and force ellipsoids for a manipulator composed of 2 DoFs and 2 segments.
Only the horizontal and vertical speeds are shown (not the rotation speeds).}
 %~ since it would require being able to draw in four dimensions.}
		   \label{sec:efort_ellipsoid}
\end{figure}

>>>>

\newcommand{\fratop}[2]{\genfrac{}{}{0pt}{}{#1}{#2}}
\newcommand{\mx}[1]{\mathbf{\bm{#1}}} 				% Matrix symbol
\newcommand{\vc}[1]{\mathbf{\bm{#1}}} 					% Vector symbol
\newcommand{\degree}{\ensuremath{^\circ}}				% define the degree symbol
\newcommand{\pder}[2]{\frac{\partial#1}{\partial#2}}		% partial derivative
\newcommand{\ppder}[2]{\frac{\partial^2 #1}{\partial#2^2}}		% second partial derivative
\newcommand{\refframe}[1]{\mbox{\textless#1\textgreater}}	% to denote a reference frame
\DeclareMathOperator*{\argmin}{\arg\!\min}				% argmin
\DeclareMathOperator*{\argmax}{\arg\!\max}				% argmax
\DeclareMathOperator*{\st}{subject\,to}					% subject to
\DeclareMathOperator*{\minimize}{minimize}				% 
\DeclareMathOperator*{\maximize}{maximize}				% 
\DeclareMathOperator*{\find}{find}						% 
\DeclareMathOperator*{\dif}{\mathrm{d}}					% d
\DeclareMathOperator*{\half}{\frac{1}{2}}					% one half
\newcommand{\equilibriumfeasibility}[0]{\glslink{equilibrium feasible}{\textit{equilibrium feasibility}}}	% matrix
\newcommand{\contactreachability}{\textit{contact reachability}}	% matrix
\newcommand{\mat}[1]{\ensuremath{\begin{bmatrix}#1\end{bmatrix}}}	% matrix
\newcommand{\rank}[1]{\text{rank}(#1)}							% rank
\newcommand{\diag}[1]{\text{diag}(#1)}							% diag
\newcommand{\x}{\ensuremath{\times}}
\newcommand{\spac}{\ensuremath{\quad}}						% alias for space in math environment
\newcommand{\dx}[0]{\ensuremath{\delta x}}					% dx
\newcommand{\du}[0]{\ensuremath{\delta u}}					% du
\newcommand{\DX}[0]{\ensuremath{\Delta X}}						% DX
\newcommand{\DU}[0]{\ensuremath{\Delta U}}						% DU
\newcommand{\T}[0]{\ensuremath{\top}}							% transpose symbol
\newcommand{\pinv}[0]{\ensuremath{\dagger}}					% pseudoinverse symbol
\newcommand{\Rv}[1]{\ensuremath{\mathbb{R}^{#1}}}				% set of real-valued vectors
\newcommand{\R}[2]{\ensuremath{\mathbb{R}^{#1\times #2}}}		% set of real-valued matrices
\newcommand{\Spd}[1]{\ensuremath{\mathbb{S}_+^{#1}}}			% set of symmetric positive-definite matrices
\newcommand{\card}[1]{\ensuremath{\left\vert{#1}\right\vert}}			% cardinality of a set
\DeclareMathOperator{\Tr}{Tr}							% trace
\newcommand{\Expect}{{\rm I\kern-.3em E}}				% expectation
\newcommand{\Normal}{\mathcal{N}}					% normal distribution
\newcommand{\Prob}[1]{\text{P}(#1)}						% probability

@@

@@

\newcommand{\gls}[1]{\textit{#1}}
\newcommand{\glslink}[2]{{#2}}

@@

\begin{figure*}[h!t!]
  \begin{center}
  \includegraphics[trim={7.0cm 0.0cm 20.0cm 0.0cm}, clip, width=\widthValue]
    {./figures/stairclimbing1.jpeg}
  \includegraphics[trim={7.0cm 0.0cm 20.0cm 0.0cm}, clip, width=\widthValue]
    {./figures/stairclimbing2.jpeg}
  \includegraphics[trim={7.0cm 0.0cm 20.0cm 0.0cm}, clip, width=\widthValue]
    {./figures/stairclimbing3.jpeg}
  \includegraphics[trim={7.0cm 0.0cm 20.0cm 0.0cm}, clip, width=\widthValue]
    {./figures/stairclimbing4.jpeg}
  \includegraphics[trim={7.0cm 0.0cm 20.0cm 0.0cm}, clip, width=\widthValue]
    {./figures/stairclimbing5.jpeg}
  \includegraphics[trim={7.0cm 0.0cm 20.0cm 0.0cm}, clip, width=\widthValue]
    {./figures/stairclimbing6.jpeg}
  \includegraphics[trim={7.0cm 0.0cm 20.0cm 0.0cm}, clip, width=\widthValue]
    {./figures/stairclimbing7.jpeg}
  \caption{
           HRP-2 in the stair climbing scenario. }
		   \label{fig:stair_robust}
  \end{center}
  \vspace{-0.5cm}
\end{figure*}

@@

\subsubsection{HyQ -- Obstacle race }
In this long scene, HyQ has to cross a 55-cm large hole, followed by a narrow ``bridge'', only 25-cm large.

%~ \begin{figure}
  %~ \centering
  %~ \includegraphics[width=0.4\linewidth]{figures/HyQ_bridge}
  %~ \caption{
           %~ HyQ crossing a narrow bridge. }
		   %~ \label{fig:HyQ_bridge}
%~ \end{figure}

%~ \begin{figure}
  %~ \centering
  %~ \includegraphics[width=1\linewidth]{figures/HyQ_obs}
  %~ \caption{
           %~ Crossing a hole contact sequence for HyQ. }
		   %~ \label{fig:HyQ_obs}
%~ \end{figure}

@@

\begin{figure}[!tbp]
  \centering
	\begin{overpic}[width=1\linewidth]{figures/ellipsoid}
		\put (8.5,1.2) {\small{Velocity ellipsoid}}
		\put (62.5,1.2) {\small{Force ellipsoid} \tiny{(scale 0.5)}}
	\end{overpic}
  \caption{Examples of velocity and force ellipsoids for a manipulator composed of 2 DoFs and 2 segments.
Only the horizontal and vertical speeds are shown (not the rotation speeds).}
 %~ since it would require being able to draw in four dimensions.}
		   \label{sec:efort_ellipsoid}
\end{figure}
